\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1.00in]{geometry}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{hyperref}

\setlength\parindent{0pt}

\setlist[itemize]{label=$\square$}
\newcommand{\done}{$\boxtimes$}

\begin{document}
2020--02--24 \\
Work done during past week: Feb 17 --- Feb 24 \\
Planned work for next week: Feb 24 --- Mar 02

\section*{Foodies}
\url{https://github.com/maryfan1106/Foodies}

\subsection*{Arman Berek's work}

\textbf{From last week}
\begin{itemize}
  \item[\done] Look at different data that can be used in the machine learning model.
  \item[\done] Discover the NYC DOHMH OpenData restaurant dataset.
\end{itemize}

%\textbf{Added mid-week}

\textbf{For this week}
\begin{itemize}
  \item Work on some frontend.
\end{itemize}


\subsection*{Mary Fan's work}

\textbf{From last week}
\begin{itemize}
  \item[\done] Work on product thinking and mock UIs.
\end{itemize}

\textbf{Added mid-week}
\begin{itemize}
  \item[\done] Work on product pitch presentation.
\end{itemize}

\textbf{For this week}
\begin{itemize}
  \item Learn React Native.
  \item Set up the initial application.
  \item Add some basic functionality to each view.
\end{itemize}


\subsection*{Jeffrey Lin's work}

\textbf{From last week}
\begin{itemize}
  \item[\done] Research the Google Places API.
\end{itemize}

\textbf{Added mid-week}
\begin{itemize}
  \item[\done] Write slides for strategy in the backend.
\end{itemize}

\textbf{For this week}
\begin{itemize}
  \item Look into importing and storing restaurant data in queryable local database.
  \item Set up database schema and initialization scripts.
\end{itemize}

\end{document}
