\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1.00in]{geometry}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{hyperref}

\setlist[itemize]{label=$\square$}
\newcommand{\done}{$\boxtimes$}

\begin{document}
\noindent{}2020--02--17 \\
Work done during  past week: Feb 10 --- Feb 17 \\
Planned work for next week: Feb 17 --- Feb 24

\section*{Foodies}
\noindent{}\url{https://github.com/maryfan1106/Foodies}

\subsection*{Arman Berek's work}
\subsubsection*{From last week}
\begin{itemize}
  \item[\done] Research machine learning algorithms suitable for our project.
\end{itemize}

%\subsubsection*{Added mid-week}

\subsubsection*{For this week}
\begin{itemize}
  \item Think about backend and pipeline for data in our suggestion engine.
\end{itemize}


\vfill
\subsection*{Mary Fan's work}
\subsubsection*{From last week}
\begin{itemize}
  \item[\done] Create rough mark-up of user interface in app.
  \item[\done] Discuss how we might store and display (temporary) user likes and dislikes.
\end{itemize}

%\subsubsection*{Added mid-week}

\subsubsection*{For this week}
\begin{itemize}
  \item Clean up drawings of mock user interface for inclusion in presentation.
\end{itemize}


\vfill
\subsection*{Jeffrey Lin's work}
\subsubsection*{From last week}
\begin{itemize}
  \item[\done] List tables and foreign-key relations we might want in our database.
\end{itemize}

\subsubsection*{Added mid-week}
\begin{itemize}
  \item[\done] Fix merge conflicts in master branch.
\end{itemize}

\subsubsection*{For this week}
\begin{itemize}
  \item Research APIs for finding food/business information near a given location.
  \item Compile project proposal presentation.
\end{itemize}

\end{document}
