\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1.00in]{geometry}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{hyperref}

\setlength\parindent{0pt}

\setlist[itemize]{label=$\square$}
\newcommand{\done}{$\boxtimes$}

\begin{document}
2020--03--02 \\
Work done during past week: Feb 24 --- Mar 02 \\
Planned work for next week: Mar 02 --- Mar 07

\section*{Foodies}
\url{https://github.com/maryfan1106/Foodies}

\subsection*{Arman Berek's work}

\textbf{From last week}
\begin{itemize}
  \item[\done] Set up the boilerplate.
\end{itemize}

%\textbf{Added mid-week}

\textbf{For this week}
\begin{itemize}
  \item Start planning and adding components.
\end{itemize}


\subsection*{Mary Fan's work}

\textbf{From last week}
\begin{itemize}
  \item[\done] Look over React Native documentation.
\end{itemize}

\textbf{Added mid-week}
\begin{itemize}
  \item[\done] Research Flutter, an alternative to React Native.
  \item[\done] Initialize the aplication.
\end{itemize}

\textbf{For this week}
\begin{itemize}
  \item Continue adding functionality to each page.
\end{itemize}


\subsection*{Jeffrey Lin's work}

\textbf{From last week}
\begin{itemize}
  \item[\done] Import and store restaurant data in queryable local SQLite database.
\end{itemize}

\textbf{Added mid-week}
\begin{itemize}
  \item[\done] Compute costs for querying price ranges and open hours from Google Places / Yelp.
\end{itemize}

\textbf{For this week}
\begin{itemize}
  \item Research using Firebase's Firestore and Cloud Functions as substitute for backend.
  \item Work on gathering price range and open hours data from Google Places / Yelp.
\end{itemize}

\end{document}
